Testing Charts: viewer's perceptual accuracy in surveys

### 2023-07-17 SDSS-2023/testing-charts-accuracy.qmd
pdf updated

```{r}
#| label: fig-aligned-unaligned
#| fig-cap: "The only difference between the two pairs of rectangles A, B and C, D is their alignment, i.e. A and C are of identical size, as are B and D. While the predominant response for the unaligned pair on the left is 'they are of the same size', more than half of the viewers respond with 'D is bigger' to the aligned pair of bars on the right."
#| fig-subcap:
#| - "**Unaligned bars**"
#| - "**Aligned bars**"
#| layout-nrow: 1
#| fig-align: "center"
#| out-width: 50%
knitr::include_graphics("images/round5-modified.PNG")
knitr::include_graphics("images/round3-modified.PNG")

```

>>>>

```{r}
#| label: fig-aligned-unaligned
#| fig-cap: "The only difference between the two pairs of rectangles A, B and C, D is their alignment, i.e. A and C are of identical size, as are B and D. When participants are asked to compare the size of these tiles in barcharts, the predominant response for the unaligned pair on the left is 'they are of the same size'. In contrast, more than half of the viewers respond with 'D is bigger' to the aligned pair of bars on the right."
#| fig-subcap:
#| - "**Unaligned bars**"
#| - "**Aligned bars**"
#| layout-nrow: 1
#| fig-align: "center"
#| out-width: 50%
knitr::include_graphics("images/round5-modified.PNG")
knitr::include_graphics("images/round3-modified.PNG")
```
